Pillar 1 - Sequential Pattern Mining

### 2019-02-13 Pillar 1 - Sequential Pattern Mining.Rmd
comments

## Sequence Rules
### Functions

```{r my_cspade function}
my_cspade <- function(data){

@@

```{r my_ruleInduction}
my_ruleInduction <- function(rules){

@@

```{r make_SR}
make_SR <- function(data, data_support, type_rule){

>>>>

## Sequence Rules
### Functions
The function `my_cspade()` applies the cspade algorithm on a set of sequential transactions with the parameters that we have chosen.
```{r my_cspade function}
my_cspade <- function(data){

@@

}
```
The function `my_ruleInduction()` creates rules from the set of frequent sequences detemined by cspade.
```{r my_ruleInduction}
my_ruleInduction <- function(rules){

@@

}
```
We encapsulate the fuctions `my_cpade`, `my_ruleInduction`, and `clean_rules` into `make_SR`
```{r make_SR}
make_SR <- function(data, data_support, type_rule){
